### 2019-08-09 paper-body.tex
Updated: Included FSM for object states and events

>>>>

\begin{figure}[hbt]
	\centering
	\resizebox{\columnwidth}{!}{
		\begin{tikzpicture}[>=stealth',shorten >=1pt,auto,node distance=2.5cm]
		\node[initial,state,accepting,align=center] (R) {$Receive$};
		\node[initial,state,accepting] (S) [below of=R] {$Inject$};
		\node[state]         (q2) [below of=S, node distance=3cm, text width=2cm, align=center] {$Intersecting$ $Boundary$};
		\node[state]         (q1) [left of=q2, node distance=4cm]  {$Host$ $Region$};
		\node[state]         (q3) [right of=q2, node distance=4cm, text width=2cm, align=center] {$Boundary$ $Traversed$};
		\node[state]         (q4) [below of=q2, node distance=4cm] {$Sent$};
		\node[state]         (q5) [right of=q4] {$Destroyed$};

		\path[->] 
		(R) edge node {} (S)
		(S) edge [bend right] node [left, text width=2cm, align=center] {No Collision} (q1)
		(S) edge node [anchor=center, text width=1.5cm, align=left] {$OBC$} (q2)
		(S) edge [bend left] node [right, text width=2cm, align=center] {Outside Owner} (q3)
		%(q1) edge [loop above] node {} (q1)
		%(q2) edge [loop left] node {} (q2)
		(q3) edge [loop below] node [above] {$BT$} (q3)
		(q1) edge node [left, text width=2cm, align=center] {$AC$} (q4)
		(q2) edge node [anchor=center, text width=2cm, align=center] {$AC$} (q4)
		(q3) edge node [anchor=center, text width=2cm, align=center] {$BT$/$AC$} (q4)

		(q1) edge [bend left] node [anchor=center, text width=1.5cm, align=center, above] {$OBC$} (q2)
		(q2) edge [bend left] node [anchor=center, text width=2cm, align=center, above] {$OBE$} (q1)
		(q3) edge [bend left] node [anchor=center, text width=2cm, align=center] {Owner Collision} (q2)
		(q2) edge [bend left] node [anchor=center, above, text width=2cm, align=center] {Owner Exit} (q3)

		(q4) edge node {} (q5)

		%(S)  edge [loop above] node {a} (S)
		%edge              node {a} (q1)
		%(q1) edge [bend left]  node {a} (S)
		%edge              node {b} (q2)
		%(q2) edge [loop above] node {b} (q2)
		%edge [bend left]  node {b} (q1)
		;
		\end{tikzpicture}
	}
\end{figure}
